### 2023-02-27 intro.qmd
update

Calcifying organisms such as coccolithophorids precipitate biogenic $CaCO_{3}$ (i.e. particulate inorganic carbon) either in the form of calcite or aragonite [@Sarmiento2006-ec] as shown in the equation below

@@

@@

This calcification occurs in surface waters, releasing $CO_{2}$ in the surrounding waters and subsequently to the atmosphere. That is why this pump is sometimes also referred to as the carbonate counter pump [@Zeebe2012-zk]. Once calcifying organisms die, their shells sink to depth and finally dissolve. Therefore, @eq-calcification shows that the carbonate pump also contributes to the observed DIC gradient, with an estimated contribution of 20% [@Sarmiento2006-ec].

@@

However, climate change is most likely going to impact the biological (e.g. shift in phytoplankton communities), physical (e.g. temperature) and chemical (e.g. nutrients availability, acidification) drivers of the BCP [@Riebesell2009-qj; @Passow2012-zh; @Bopp2013-jx] whose long-term carbon sequestration capacity remains uncertain [@Passow2012-zh; @Turner2015-af; @DeVries2022-of; @Wilson2022-bf].

@@

To the best of my knowledge, the most emblematic case of discussions around this question is the mineral ballast hypothesis [@De_La_Rocha2007-yi]. Mineral ballasting consists in the inclusion of biominerals such as opal (i.e. silicate) and calcite or lithogenic material such as dust that are thought to increase $\Delta\rho$ on the one hand and protect them from microbial degradation on the other hand [@Armstrong2001-rz; @Francois2002-uc; @Klaas2002-kn]. However, several studies argue otherwise. @Passow2004-re stipulates that biominerals could instead be collected (i.e. scavenged) and transported downwards by sinking aggregates. @Ploug2008-qk did not measure significant differences in microbial degradation of non ballasted vs. ballasted material. Finally, @Passow2006-hw developed an experiment to investigate the relationship between the incorporation of biominerals into aggregates and their sinking speed. They showed that this relationship was not straigthforward due to the fact that the inclusion of biominerals fragmented aggregates into smaller but denser particles which could either decrease (smaller size) or increase (denser particles) their sinking speed.

>>>>

Calcifying organisms (mostly coccolithophores, foraminifera and pteropods) produce particulate inorganic carbon (PIC) by precipitating biogenic $CaCO_{3}$ [@Sarmiento2006-ec]

@@

to form calcite structures such as calcite platelets (coccoliths), calcite shells or spines [@Neukermans2023-vl].

@@

This calcification occurs in surface waters, releasing $CO_{2}$ in the surrounding waters and subsequently to the atmosphere (0.26 - 1.19 Pg C year$^{-1}$ following @Neukermans2023-vl). That is why this pump is sometimes also referred to as the carbonate counter pump \[@Zeebe2012-zk\]. However, the dissolution of $CaCO_{3}$ mainly occurs at depth and thus increases the DIC concentration (@eq-calcification). In all, @Sarmiento2006-ec estimated that the carbonate pump contributes to 20% of the observed DIC gradient.

@@

However, climate change is most likely going to impact the biological (e.g. shift in phytoplankton communities), physical (e.g. temperature) and chemical (e.g. nutrients availability, acidification) drivers of the BCP [@Riebesell2009-qj; @Passow2012-zh; @Bopp2013-jx] whose long-term carbon sequestration capacity remains uncertain [@Passow2012-zh; @Turner2015-af; @DeVries2022-of; @Henson2022-hg ; @Wilson2022-bf].

@@

To the best of my knowledge, the most emblematic case of discussions around this question is the mineral ballast hypothesis [@De_La_Rocha2007-yi]. Mineral ballasting consists in the inclusion of biominerals such as opal (i.e. silicate) and calcite or lithogenic material such as dust that are thought to increase $\Delta\rho$ on the one hand and protect them from microbial degradation on the other hand [@Armstrong2001-rz; @Francois2002-uc; @Klaas2002-kn]. However, several studies argue otherwise. @Passow2004-re stipulates that biominerals could instead be collected (i.e. scavenged) and transported downwards by sinking aggregates. @Ploug2008-qk did not measure significant differences in microbial degradation of non ballasted vs. ballasted material. Finally, @Passow2006-hw developed an experiment to investigate the relationship between the incorporation of biominerals into aggregates and their sinking speed. They showed that this relationship was not straigthforward due to the fact that the inclusion of biominerals fragmented aggregates into smaller but denser particles which could either decrease (smaller size) or increase (denser particles) their sinking speed. Other studies on the ballasting effect have been published since but even 20 years after its proposition, no global ballasting mechanism has been found [@Neukermans2023-vl].

### 2023-02-27 observingCarbonCycle.qmd
update

I will hereafter briefly describe a non exhaustive list of biogeochemical models to illustrate how the export production can be estimated using the $e-ratio$.

@@

When we compare the $e-ratio$ maps (@fig-export-ratios) or the carbon export estimations of just six biogeochemical models (see @sec-biogeochem-models), we already observe strong differences. In my opinion, it means at least two things. On the one hand, we are seeing an increase in model complexity from empirical models to data-assimilated inverse models. At the same time, we also gathered more observational data as well as a deeper understanding of the BCP (@sec-a-new-paradigm-for-the-bcp) that allow us to better represent its underlying processes. On the other hand, each degree of complexity propagates more and more uncertainty (@fig-bgc-models) that we need to account for in the results.

@@

@@

This framework will hopefully address the questions raised so far, i.e., better understand the underlying drivers of each component of the BCP, decouple the contribution of each pump to the observed downward carbon flux lengthily attributed to the BGP and estimates of carbon sequestration \[@Boyd2019-ez; @Passow2012-zh\] as well as close the ocean carbon budget \[@Burd2010-hc\].

@@

1.  BGC-Argo floats equipped with a UVP6 and the zooplankton recognition algorithm are able to classify particles larger than 0.6 mm. However, these AUVs are limited in terms of their battery life. They are typically deployed for several years, which requires special attention to the energy consumption of each sensor. In @sec-uvp-ia I will therefore describe the methodology used to develop the zooplankton classification model for the UVP6 accounting for energy limitations.
2.  4 BGC-Argo floats equipped with both a transmissometer and a UVP6 were deployed for the first time in the Labrador Sea in late May 2022 to investigate the post-spring bloom and its associated POC fluxes. In @sec-case-study-labrador-sea, I will show how transmissometers used as OSTs compare with PSDs measured by UVP6s as well as investigate the link between small and big particle fluxes derived by both instruments.
3.  Many studies have assumed that carbon sequestration only occurs in the deep ocean (typically 1000 m). In @sec-to-do, I reassess the global sequestration ($\geq$ 100 years) of the BCP and its components by using a continuous approach to carbon storage as opposed to the common view of long-term sequestration below a fixed reference depth.

>>>>

I will hereafter briefly describe a non exhaustive list of biogeochemical model types to illustrate how the export production can be estimated using the $e-ratio$.

@@

When we compare the $e-ratio$ maps (@fig-export-ratios) or the carbon export estimations of only six biogeochemical models (see @sec-biogeochem-models), we already observe strong differences. On the one hand, we are seeing an increase in model complexity from empirical models to data-assimilated inverse models. At the same time, we also gathered more observational data as well as a deeper understanding of the BCP (@sec-a-new-paradigm-for-the-bcp) that allows us to better represent its underlying processes. On the other hand, each degree of complexity inevitably accumulates more uncertainty due to the increasing number of processing and modeling steps (@fig-bgc-models).

@@

From the data we feed models with to uncertainties caused by missing or poorly misunderstood processes, current BCP models still disagree on the estimation of carbon export both currently and in response to climate change [@Henson2022-hg]. However, the ongoing increase in deployments of autonomous platforms and the development of new sensors is providing new opportunities to enhance the parametrization of key biogeochemical processes to better estimate carbon export and sequestration.

@@

This framework will hopefully address the questions raised so far, i.e., better understand the underlying drivers of each component of the BCP, decouple the contribution of each pump to the observed downward carbon flux lengthily attributed to the BGP and estimates of carbon sequestration [@Boyd2019-ez; @Passow2012-zh] as well as close the ocean carbon budget [@Burd2010-hc].

@@

1.  BGC-Argo floats equipped with a UVP6 and the zooplankton recognition algorithm are able to classify particles larger than 0.6 mm. However, these AUVs are limited in terms of their battery life. They are typically deployed for several years, which requires special attention to the energy consumption of each sensor. In @sec-uvp-ia I will therefore describe the methodology used to develop the zooplankton classification model for the UVP6 accounting for energy limitations.
2.  4 BGC-Argo floats equipped with both a transmissometer and a UVP6 were deployed for the first time in the Labrador Sea in late May 2022 to investigate the post-spring bloom and its associated POC fluxes. In @sec-case-study-labrador-sea, I will show how transmissometers used as OSTs compare with PSDs measured by UVP6s as well as investigate the link between small and big particle fluxes derived by both instruments.
3.  Many studies have assumed that carbon sequestration only occurs in the deep ocean (typically 1000 m). In @sec-to-do, we reassess the global sequestration ($\geq$ 100 years) of the BCP and its components by using a continuous approach to carbon storage as opposed to the common view of long-term sequestration below a fixed reference depth.
